Changes in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2020-08-18 analysis/paper/paper.Rmd
GP added elevation plot and reference

ggplot(mydata_ages, 
       aes(x = age_ka,
           y = altitude.m._of_main_layer,
       color = as.factor(has_sp))) +
  geom_point(size = 3) +
  xlab("Age of occupation (ka)") +
  ylab("Elevation above sea level (m)") +
  geom_smooth(se = FALSE) +
  scale_colour_discrete(name = "Contains\nstemmed\npoints?") +
  theme_minimal(base_size = 16)

>>>>

elevation_sp_sub_plot <- 
ggplot(kasv_tidy,
       aes(has_sp, 
           altitude.m._of_main_layer)) +
  geom_boxplot() +
  theme_bw(base_size = 8)  +
  labs(x = "Stemmed points present",
       y = "Elevation")

elevation_sp_main_plot <- 
ggplot(mydata_ages, 
       aes(x = age_ka,
           y = altitude.m._of_main_layer,
       color = as.factor(has_sp))) +
  geom_point(size = 3) +
  xlab("Age of occupation (ka)") +
  ylab("Elevation above sea level (m)") +
  geom_smooth(se = FALSE) +
  scale_colour_discrete(name = "Contains\nstemmed\npoints?") +
  theme_minimal(base_size = 16)

library(cowplot)
ggdraw(elevation_sp_main_plot) +
  draw_plot(elevation_sp_sub_plot, 
            .475, .57, 
            .25, .32) 
```
